Pleiades: Interactive Composing Tools for Vega-Lite Charts

### 2019-06-11 paper/paper.tex
use `` as starting double quote

To work with Pleiades, users can firstly add Vega-Lite specs that they are working
with to the left sidebar by clicking "NEW SPEC", then type in the Vega-Lite spec,
and then save.

@@

To edit a composed view, users can select a view in the working area. Then, click
"EDIT" configure the properties of the selected view.

Users can always redo or undo any action if they make mistakes by clicking "UNDO"
or "REDO".

>>>>

To work with Pleiades, users can firstly add Vega-Lite specs that they are working
with to the left sidebar by clicking ``NEW SPEC'', then type in the Vega-Lite spec,
and then save.

@@

To edit a composed view, users can select a view in the working area. Then, click
``EDIT'' configure the properties of the selected view.

Users can always redo or undo any action if they make mistakes by clicking ``UNDO''
or ``REDO''.
